\plaintitle

### 2017-06-16 papers/IoT2017/analysis.tex
updates

In this section, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements that were formulated earlier.

\subsection{Security}
Satisfaction of the security requirements follows from:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item non-malleability of transactions in the distributed ledger,
\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
\item and tamper-resistance of smart meters.
\end{itemize}
Together, these properties ensure that only the right entities may create and sign a transaction, that transactions adhere to the rules of the trading process, and that transactions cannot be tampered with.
Due to lack of space, we leave a detailed discussion and proof for future work.

\subsection{Safety}
Next, we demonstrate that faulty or malicious prosumers cannot trade excessive amounts of energy if normal prosumers follow the rules of the trading process. 
%
First, we can show that the net amount of energy sold by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i$.
By definition, the amount of energy sold is less than or equal to the amount of EPA obtained by prosumer $i$.
A prosumer can obtain EPA either by withdrawing from its smart meter or by purchasing form another prosumer.
From its smart meter, prosumer $i$ can withdraw at most $\field{MAXEPA}_i$. % amount of EPA.
The prosumer may also buy EPA from another prosumer; however, this constitutes buying energy, which decreases the net amount of energy sold with the same amount.
%However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed $\field{MAXEPA}_i$.
By extending the argument, we can show that the net amount of energy sold by a group of prosumers~$G$ cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.
Similarly, we can show that the net amount of energy bought by a group of prosumers $G$ cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

Second, we can show that the amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

\subsection{Privacy}
Due to the use of communication anonymity and mixing services, members of a microgrid can observe only the amount of assets withdrawn by a prosumer from its smart meter. % the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, they do not reveal the actual amount of assets traded by the prosumer.
If a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
Note that even if a prosumer does not wish to trade, it should always withdraw, mix, and deposit the same amount of assets.
Otherwise, the lack (or varying amount) of withdrawal would leak information.

As for the DSO, it receives the same information from the smart meter as in a non-transactive smart grid (i.e., amount of energy produced and consumed).
Since trading is anonymous, the DSO learns only the financial balance of the prosumer, which is necessary for billing.

However, we can provide an even higher-level of privacy.
Since price policies are recorded on the ledger, which the smart meters may read, each prosumer's smart meter may calculate and send the prosumer's monthly bill to the DSO, without revealing the prosumer's energy consumption or production.
Meanwhile, the DSO can still obtain very detailed load information (including predictions) for the microgrid from the bid storage and the trades recorded on the ledger.

>>>>

This section presents a semi-formal analysis of our proposed solution
and show that it satisfies the security, safety, and privacy
requirements formulated in earlier sections.

\subsection{Security}
Satisfaction of the security requirements follows from:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item non-malleability of transactions in the distributed ledger,
\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
\item and tamper-resistance of smart meters.
\end{itemize}
Together, these properties ensure that only the right entities may
create and sign a transaction, that transactions adhere to the rules
of the trading process, and that transactions cannot be tampered
with.\footnote{Due to lack of space, we leave a detailed discussion
  and proof for future work.}

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading process.
%
First, we show that the net amount of energy sold by prosumer $i$ for
each timestep is at most $\field{MAXEPA}_i$.  By definition, the
amount of energy sold is less than or equal to the amount of EPA
obtained by prosumer $i$.  A prosumer can obtain EPA either by
withdrawing from its smart meter or by purchasing form another
prosumer.  From its smart meter, prosumer $i$ can withdraw at most
$\field{MAXEPA}_i$.
% amount of EPA.
Although the prosumer may also buy EPA from another prosumer, this
constitutes buying energy, which decreases the net amount of energy
sold with the same amount.
%However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed
$\field{MAXEPA}_i$.  By extending the argument, we show that the net
amount of energy sold by a group of prosumers~$G$ cannot exceed
$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we show that the net
amount of energy bought by a group of prosumers $G$ cannot exceed
$\sum_{i \in G} \field{MAXECA}_i$.

We also show that the total amount of energy bids (or asks) posted at
the same time by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
net energy sold or bought, since prosumer $i$ may purchase
$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
from other prosumers, and then post an energy ask (or bid) in the
amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

\subsection{Privacy}
Due to our use of communication anonymity and mixing services, members
of a microgrid can observe only the amount of assets withdrawn by a
prosumer from its smart meter.
% the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, they do not reveal the
actual amount of assets traded by the prosumer.  If a prosumer does
not wish to trade, therefore, it can anonymously deposit its assets to
a random address that was freshly generated by its smart meter.  Even
if a prosumer does not wish to trade, however, it should always
withdraw, mix, and deposit the same amount of assets.  Otherwise, the
lack (or varying amount) of withdrawal would leak information.

As for the DSO, it receives the same information from the smart meter
as in a non-transactive smart grid (\em{i.e.}, amount of energy
produced and consumed).  Since trading is anonymous, the DSO learns
only the financial balance of the prosumer, which is necessary for
billing.  However, we can provide an even higher-level of privacy.  In
particular, since price policies are recorded on the ledger (which the
smart meters may read), each prosumer's smart meter may calculate and
send the prosumer's monthly bill to the DSO, without revealing the
prosumer's energy consumption or production.  Meanwhile, the DSO can
still obtain detailed load information (including predictions) for the
microgrid from the bid storage and the trades recorded on the ledger.

### 2017-06-16 papers/IoT2017/related.tex
updates

%\subsection{Smart Grid and Meter Privacy}
% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
% http://www.comm.toronto.edu/~akhisti/sm.pdf
% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart grids. In addition to both old and new security threats, such as energy theft and smart-meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}. Several approaches have been investigated as potential means to provide privacy protections for smart grid users.

Some approaches look to the use of protocols and/or frameworks to help protect privacy. Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart-meter data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter. The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with a particular smart meter.

Additionally, other approaches such as additional hardware components are explored for potential privacy gains. Varodayan and Khisti study using a rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}. They show that stochastic battery policies may leak 26\% less information than a best-effort policy, which holds the output load constant whenever possible. Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. % They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.

Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading. In other words, while earlier results protected the prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.

A key element of our approach is the ability to distribute information among peers. For that purpose, we rely on the use of blockchains. 
As blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels, whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. However, this paper focuses on theoretical aspects of our implementation and as such, any one of the distributed ledgers provide the required capabilities.

>>>>

%\subsection{Smart Grid and Meter Privacy}
% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
% http://www.comm.toronto.edu/~akhisti/sm.pdf
% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart
grids. In addition to old and new security threats (such as energy
theft and smart-meter malware), McDaniel and McLaughlin discuss the
privacy concerns of energy usage profiling that smart grids could
potentially enable~\cite{mcdaniel2009security}. Several approaches
have been investigated as potential means to provide privacy
protections for smart grid users.

Some approaches look to the use of protocols and/or frameworks to help
protect privacy. Rajagopalan et al.\ use tools from information theory
to present a framework that abstracts both the privacy and the utility
requirements of smart-meter
data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework
leads to a novel tractable privacy-utility tradeoff problem with
minimal assumptions. Efthymiou and Kalogridis describe a method for
securely anonymizing frequent electrical metering data sent by a smart
meter~\cite{efthymiou2010smart}. Their approach is based on the
observation that frequent metering data may be required by an energy
distribution network for operational reasons, but it may not
necessarily need to be attributable to a specific smart meter. The
authors describe a method that provides a third-party escrow mechanism
for authenticated anonymous meter readings, which are hard to
associate with a particular smart meter.

Additionally, other approaches such as additional hardware components
are explored for potential privacy gains. Varodayan and Khisti study
using a rechargeable battery for partially protecting the privacy of
information contained in a household's electrical load
profile~\cite{varodayan2011smart}. They show that stochastic battery
policies may leak 26\% less information than a best-effort policy,
which holds the output load constant whenever possible. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy.
% They show that there exists a trade-off between the information
% leakage rate and the wasted energy rate, and study the impact of the
% energy harvesting rate and the size of the storage device on this trade-off.

Our solution extends this earlier work by considering a decentralized
IoT system for transactive energy, and addressing the novel privacy
threat posed by trading. In particular, while earlier results
protected the prosumers' privacy from the DSO, we protect privacy from
other prosumers as well as from outside attackers.

A key element of our approach is the ability to distribute information
among peers via blockchains.  As blockchain technology develops and
matures, new frameworks, services, and protocols are being developed
to leverage blockchain's distributed ledger. For example, Hyperledger
Fabric is a platform for distributed ledger solutions, which was
designed to support pluggable implementations of different
components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is
decentralized system, in which transactions are sent over a network of
micropayment channels, whose transfer of value occurs
off-blockchain~\cite{poon2016bitcoin}. Since this paper focuses on
theoretical foundations of our implementation, any of these
distributed ledgers provide the required capabilities.

### 2017-06-16 papers/IoT2017/services.tex
updates

In this subsection, we describe the various services that are provided in our system. %on which transactions are built and which build on transactions.
We have already discussed the distributed ledger, which permanently stores valid transactions.
Now, we will introduce the anonymous communication service, the mixing service for transaction anonymity, the anonymous bid storage, and smart-meter based billing.

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build all the other services in our system.
Without this communication layer, transactions and bids could be easily de-anonymized based on their sources' network identifiers (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can be built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication identifiers in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
Fortunately, most distributed ledgers allow users to easily generate new addresses %\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum. 
%Specifically, we use the term address to denote a possible destination for asset transfers. 
%Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
at random.
Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.

To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
In practice, a mixing service can be implemented using multiple approaches.
The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party. %, which would constitute a single point of failure.
Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.

\begin{comment}
We must provide prosumers with the ability to create and publish transactions anonymously.
More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.

@@

\subsubsection{Bidding Anonymity}
Finally, we must enable prosumers to anonymously post energy bids and asks on the bid storage service.
An anonymous bid (or ask) contains an ECA (or EPA), a price, and an anonymous communication identifier (e.g., Tor hidden service), which can be used to contact the bidding (or asking) prosumer.
To enforce safety requirements, the bid storage service must verify that the prosumer actually owns the asset to be traded.
To this end, the prosumer first has to prove that it controls the anonymous address where the asset is stored, which can be performed in multiple ways.
In many distributed ledgers, an address represents a public key, and controlling means knowing the corresponding private key.
In this case, the prosumer can prove that it controls an address by signing a challenge, which was freshly generated by the service, with the private key of the address.
Alternatively, the prosumer may also prove control by transferring zero amount of assets to a random address that was freshly generated by the service.

@@

\subsubsection{Smart-Meter Based Billing}
Once a prosumer has finished trading, it deposits all of its EPA, ECA, and FA to the smart meter, by transferring them to an anonymous address generated by the smart meter.
Later, during timeslot $t$, the smart meter measures the amount of energy actually consumed (or produced) by the prosumer using physical sensors.
Then, the meter can compute the prosumer's bill for timeslot $t$, which is to be paid to the DSO, as follows.

The energy consumption balance $E_i^t$ of prosumer $i$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
 & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} \\
 & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} .
% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.

The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which is to be paid by the prosumer to the DSO, is
\begin{align*}
B_i^t = &  \text{FA withdrawn by $i$ during $t$} - \text{FA deposited by $i$ during $t$} \\
 & + \begin{cases}
- E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
 E_i^t \cdot \field{priceConsumption} & \text{ otherwise,} 
\end{cases}
\end{align*}
where {\field{priceProduction}} and {\field{priceConsumption}} are the prices set by the latest regulatory transactions for timeslot $t$.

>>>>

We now describe the various services that are provided in our system.
%on which transactions are built and which build on transactions.
Earlier we discussed the distributed ledger, which permanently stores
valid transactions.  Below we introduce the anonymous communication
service, the mixing service for transaction anonymity, the anonymous
bid storage, and smart-meter based billing.

\subsubsection{Communication Anonymity}
The anonymous communication layer is the infrastructure upon which all
other services in our system are built.  Without this communication
layer, transactions and bids could be easily de-anonymized based on
their sources' network identifiers (\em{e.g.}, IP or MAC addresses).

We employ well-known and widely used techniques for anonymous
communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
To build an onion network, the smart meters, prosumers, and other
devices can act as onion routers, and the list of onion routers in a
microgrid can be published on the ledger.  In practice, this service
is built on
%In our first implementation, we can use
the free and open-source Tor software with private Directory
Authorities.  In this case, anonymous communication identifiers in
bids and asks correspond to public-keys that identify Tor hidden
services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary, but not sufficient, for
anonymous trading. In particular, if prosumers used their own accounts
to transfer assets, their trades would not be anonymous.  Fortunately,
most distributed ledgers allow users to easily generate new addresses
%\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
%Specifically, we use the term address to denote a possible destination for asset transfers. 
%Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
at random, so they are anonymous in the sense that no one can tell who
generated them.  If prosumers simply transferred assets to these
addresses, however, they could be easily de-anonymized by tracing the
assets back to the prosumers.

To prevent this de-anonymization, prosumers transfer assets to their
anonymous addresses through a \emph{mixing service}.  The mixing
service prevents tracing assets back to their original owners by
mixing together multiple incoming transfers and multiple outgoing
transfers. This service thus hides the connections between the
prosumers and the anonymous addresses.

A mixing service can be implemented using multiple approaches.  The
simplest one is to use a \emph{trusted third party}, called a
cryptocurrency tumbler, which can receive and send assets.  Anonymity
in this case, however, depends on the trustworthiness and reliability
of the third party, who could easily de-anonymize the addresses.  A
more secure approach is to used decentralized protocols, such as
CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.  These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party.
%, which would constitute a single point of failure.
Some newer cryptocurrencies, such as
Zerocoin~\cite{miers2013zerocoin}, provide built-in mixing services,
which are often based on cryptographic principles and proofs.

% Abhishek, what does \begin{comment} mean in this context?
\begin{comment}
We must provide prosumers with the ability to create and publish
transactions anonymously.  More specifically, prosumers should be able
to purchase or sell energy without revealing their identity; however,
these transaction must also be verifiable and enforceable.

@@

\subsubsection{Bidding Anonymity}
Prosumers must be able to anonymously post energy bids and asks on the
bid storage service.  An anonymous bid (or ask) contains an ECA (or
EPA), a price, and an anonymous communication identifier (\em{e.g.},
Tor hidden service), which can be used to contact the bidding (or
asking) prosumer.  To enforce safety requirements, the bid storage
service must verify that the prosumer actually owns the asset to be
traded.  To this end, the prosumer first has to prove that it controls
the anonymous address where the asset is stored, which can be
performed in multiple ways.

In many distributed ledgers, an address represents a public key, and
controlling means knowing the corresponding private key.  In this
case, the prosumer can prove that it controls an address by signing a
challenge, which was freshly generated by the service, with the
private key of the address.  Alternatively, the prosumer may also
prove control by transferring zero amount of assets to a random
address that was freshly generated by the service.

@@

\subsubsection{Smart-Meter Based Billing}
After a prosumer has finished trading, it deposits all of its EPA,
ECA, and FA to the smart meter by transferring them to an anonymous
address generated by the smart meter.  Later, during timeslot $t$, the
smart meter measures the amount of energy actually consumed (or
produced) by the prosumer using physical sensors.  The meter can then
compute the prosumer's bill for timeslot $t$, which will be paid to
the DSO, as follows.

The energy consumption balance $E_i^t$ of prosumer $i$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
 & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} \\
 & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} .
% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Consumption assets are only used to enforce security and safety
requirements, but are not used directly for billing.

The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which will be paid
by the prosumer to the DSO, is
\begin{align*}
B_i^t = &  \text{FA withdrawn by $i$ during $t$} - \text{FA deposited by $i$ during $t$} \\
 & + \begin{cases}
- E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
 E_i^t \cdot \field{priceConsumption} & \text{ otherwise,} 
\end{cases}
\end{align*}
where {\field{priceProduction}} and {\field{priceConsumption}} are the
prices set by the latest regulatory transactions for timeslot $t$.
